### 2021-07-03 docs/manuscript/manuscript.tex
Mention sensibility to morphogenetic field size

Although the topology 9 consists of only two genes, its mechanism of expression
is dynamically more complex than that of other topologies such as the simple
I3-FFL. Initially the expression pattern of the gene A is uniform in the
morphogenetic field, but later it is shaped by the morphogen gradient in such a
way that two important events occur, in first place the overall expression
level of the gene A is decreased by the inhibition of the morphogen, releasing
gene C from its repression by gene A; in second place, it appears a
non-homogeneous spatial distribution in which gene A is expressed at higher
levels in the cells at the rightmost part of the morphogenetic field.\\

@@

This is a complex mechanism described by the first time in this study, and it
would be interesting to study its feasibility and possible implementation in
synthetic gene regulatory networks.

@@

>>>>

Although the topology 9 consists of only two genes, its mechanism of expression
is dynamically more complex than that of other topologies such as the simple
I3-FFL; however, and despite the fact that the Gierer-Meinhardt model form
patterns that scale with tissue size~\cite{shoaf1984}, we found that topology 9
was more sensible to changes in the morphogenetic field size than those
topologies based on I3-FFL (\nameref{S2_Table}),
indicating that the additional regulatory interactions need to be fine-tuned
depending on the number of cells in the field.\\

In the mechanism of expression of topology 9 the expression pattern of the
gene A is initially uniform in the
morphogenetic field, but later it is shaped by the morphogen gradient in such a
way that two important events occur, in first place the overall expression
level of the gene A is decreased by the inhibition of the morphogen, releasing
gene C from its repression by gene A; in second place, it appears a
non-homogeneous spatial distribution in which gene A is expressed at higher
levels in the cells at the rightmost part of the morphogenetic field.\\

@@

This is a complex mechanism remindful of the Gierer-Meinhardt model, but
described by the first time in this study in the context of multiple morphogen
inputs, and it would be interesting to study its feasibility and possible
implementation in synthetic gene regulatory networks.

@@

\paragraph*{S2 Table.}
\label{S2_Table}
{\bf Average fitness of each topology in different morphogenetic fields.}
The average fitness by topology is reported for morphogenetic fields with 10, 20,
40 and 50 cells.
